Artin Group Presentations Arising from Cluster Algebras

### 2014-10-11 Paper.tex
New Bibliography

\usepackage{amsmath,amssymb,amsthm, MnSymbol}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage[mathscr]{euscript}

@@

\bibliography{References}
\bibliographystyle{alpha}

>>>>

\usepackage{amsmath,amssymb,amsthm, MnSymbol}
\usepackage{enumerate}
\usepackage[mathscr]{euscript}

@@

\begin{thebibliography}{9}
\bibitem{BM13}
Michael Barot and Robert J. Marsh,
``Reflection Group Presentations Arising from Cluster Algebras,''
arXiv: 1112.2300v2, 2013

\bibitem{C06}
Ruth Charney,
``An Introduction to Right-Angled Artin Groups,''
arXiv:math/0610668, 2006

\bibitem{FT13}
A. Felikson and P. Tumarkin,
``Coxeter groups and their quotients arising from cluster algebras,''
arXiv:1307.0672v2, 2013

\bibitem{FZ02}
Sergey Fomin and Andrei Zelevinsky,
``Cluster Algebras I: Foundations,''
\textit{J. Amer. Math. Soc.}, 15, 497-529, 2002

\bibitem{FZ03}
Sergey Fomin and Andrei Zelevinsky,
``Cluster Algebras II: Finite type classification,''
\textit{Invent. Math.}, 154, 63-121, 2003

\bibitem{FN61}
R. Fox and L. Neuwirth,
``The Braid Groups,''
\textit{Mathematica Scandinavica}, 119-126, 1961

\bibitem{GM14}
Joseph Grant and Robert J. Marsh
``Braid groups and quiver mutation,''
arXiv:1408.5267, 2014

\bibitem{Q14}
Y. Qiu,
``On the spherical twists on 3-Calabi-Yau categories from marked surfaces,''
arXiv:1407.0806, 2014

\end{thebibliography}
